---
title: "Wind optim CH WP 1"
author: "R.Spielhofer"
date: "March - April 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
install.packages("stars")
install.packages("mapview")
install.packages("Rpostgres")





require(mapview)
require(raster)
require(rgdal)
require(dplyr)
require(ggplot2)
require(sf)
require(Hmisc)
require(tmap)
require(tmaptools)
require(DBI)
require(RPostgreSQL)
require(rpostgis)

library(stars)

rasterOptions(progress="T")#progress bar 
opar <- par()
cur_dat<-Sys.Date()

##general coordinate system
coord<-make_EPSG()
coord<-coord %>%
  filter(code == 21781)


##POSTGIS DB connection for the files (ETH)
con<- dbConnect("PostgreSQL", dbname = "publication_3_fin", host = "localhost", user = "postgres", password
                        = "reto89LLSIMI")

```

# Description of WP PEPP

This workpackages describes the calculation of the spatial explicit PEPP "physical energy production potential". We consider the parameters for a Vestas V112-3.0 and a Vestas V90-2.0 wind turbine with a hub height of 120 and 100 meters above ground. The Vestas V112-3.0 has a rotor diameter of 112 meters, the V90-2.0 90 meters. Both wind turbines have a cut-on wind speed at 3 m/s and a cut-off at 25 m/s. In order to calculate the spatial explicit power we consider the airdensity (p), approximated with the altitude, the average weibul parameters A and k. We further consider the power curve of both turbines which is dependent on the wind speed.   

## Topography and air density

As a first step, the topographic elevation model of Switzerland (dem_200), with a cell size of 200 meters is imported. 
```{r}

dem_200<-raster("input_data/200_DEM.tif")
dem_200<-projectRaster(dem_200, crs="+init=epsg:21781")
mapview(dem_200)

crs(dem_200)
```


Subsequently, the airdensity (p) is approximated with the following formula, where x represents the meters a s.l. from the DEM.
```{r}
airdens <- function(x) { 1.247015*exp(-0.000104*x) }

```


The new raster "airdensity_200" contains airdensity values for each raster cell.

```{r}
# transform the dem_200 into an approximate air density raster
airdens_200 <- calc(dem_200, fun=airdens)
crs(airdens_200)
writeRaster(airdens_200,filename="intermediate_steps/1_wp/200_airdens",overwrite=T)

```

Altitude raster and corresponding air densities
```{r pressure, echo=FALSE}
#mapview(dem_200, maxpixels=2344496)| airdens_200

```

## wind speed depending on hub heights
To calculate the wind power in each raster cell we consider the spatial explicit weibull parameters A and k (provided by the wind data of meteotest). Both parameters are dependent from the height above ground (100,125 and 150m meters in our case).

```{r}

wind_dat_path<-"input_data/wind_weibull"
outpath<-"intermediate_steps/1_wp/wind"

#A parameter of weibull distribution 150 meter wind speeds
A150<-raster(paste(wind_dat_path,"A_150.tif",sep="/"))
#reproject and resoltion
A150 <- projectRaster(A150, crs = crs(dem_200), res = 200 )
#resampling to adjust the extent
A150_200<-resample(A150, dem_200, method="bilinear")
writeRaster(A150_200,filename=paste(outpath,"A150_200.tif",sep = "/"),overwrite=T)

#k parameter of weibull distribution 125 meter wind speeds
k150<-raster(paste(wind_dat_path,"k_150.tif",sep="/"))

#reproject and resoltion
k150 <- projectRaster(k150, crs = crs(dem_200), res = 200 )
#resampling to adjust the extent
k150_200<-resample(k150, dem_200, method="bilinear")
writeRaster(k150_200,filename=paste(outpath,"k150_200.tif",sep = "/"),overwrite=T)


#A parameter of weibull distribution 125 meter wind speeds
A125<-raster(paste(wind_dat_path,"A_125.tif",sep="/"))

#reproject and resoltion
A125 <- projectRaster(A125, crs = crs(dem_200), res = 200 )
#resampling to adjust the extent
A125_200<-resample(A125, dem_200, method="bilinear")
writeRaster(A125_200,filename=paste(outpath,"A125_200.tif",sep = "/"),overwrite=T)

#k parameter of weibull distribution 125 meter wind speeds
k125<-raster(paste(wind_dat_path,"k_125.tif",sep="/"))

#reproject and resoltion
k125 <- projectRaster(k125, crs = crs(dem_200), res = 200 )
#resampling to adjust the extent
k125_200<-resample(k125, dem_200, method="bilinear")
writeRaster(k125_200,filename=paste(outpath,"k125_200.tif",sep = "/"),overwrite=T)


## and the same procedure for the 100m above ground
A100<-raster(paste(wind_dat_path,"A_100.tif",sep="/"))

A100 <- projectRaster(A100, crs = crs(dem_200), res = 200 )
A100_200<-resample(A100, dem_200, method="bilinear")
writeRaster(A100_200,filename=paste(outpath,"A100_200.tif",sep = "/"),overwrite=T)

#k parameter of weibull distribution 100 meter wind speeds
k100<-raster(paste(wind_dat_path,"k_100.tif",sep="/"))

#reproject and resoltion
k100 <- projectRaster(k100, crs = crs(dem_200), res = 200 )
#resampling to adjust the extent
k100_200<-resample(k100, dem_200, method="bilinear")
writeRaster(k100_200,filename=paste(outpath,"k100_200.tif",sep = "/"),overwrite=T)
```

## cp 
According to https://www.wind-turbine-models.com/turbines and thanks to philipp mattle from emch and berger, we extracted power efficiency values cp for Vestas V150-4.2 (150m hub height) E-138-3.5 (125m hub height) and E-82-2.0 (100m hub height) for each wind speed between 0 and 30 m/s.
```{r}
#cp_stored in DB

pow_curve<-dbReadDataFrame(con,c("wind_input","pow_curve")) 
```

## Spatial explicit power calculation for wind turbines
The funtions "tot" take the airdensity, the efficency parameter cp, the mean wind speed for i intervalls and the two site specific weibull parameters A and k as inputs. In a loop between 0 and 30 all probabilities that the wind speeds will occur according to the specific weibull distribution is calculated and multiplied by the total amount of hours per year.

```{r}
cur_dat<-Sys.Date()
outpath<-"intermediate_steps/1_wp/pot_ener_CH"

#125 meters above ground with E138-4.2 power curve (67m radius) with an efficiency parameter of 0.8 (mail philipp 12.5.20)
fun_totE138<-function(airdens_200,cpe138,i,k,A){0.8*(0.5*(airdens_200*(67^2*pi)*i^3)*cpe138)/1000*(k/A*((i/A)^(k-1))*exp(1)^(-(i/A)^(k)))*8760}

WEA_pow_tot125<-reclassify(A125_200, c(-Inf,Inf,0))
for(i in 1:29){
  mean_wind<-reclassify(A125_200, c(-Inf,Inf,i))
  cp1<-pow_curve$E.138_cp[i]
  cpe138<-reclassify(A125_200, c(-Inf,Inf,cp1))
  rSTACK<-stack(airdens_200,cpe138,mean_wind,k125_200,A125_200)
  WEA_pow1 <-overlay(rSTACK, fun=fun_totE138, unstack=TRUE)
  WEA_pow_tot125<-WEA_pow_tot125+WEA_pow1
}

#100 meters above ground with E82 2.0 power curve (39m radius) with an efficiency parameter of 0.8 (mail philipp 12.5.20)
fun_totE82<-function(airdens_200,cpe82,i,k,A){0.8*(0.5*(airdens_200*(39^2*pi)*i^3)*cpe82)/1000*(k/A*((i/A)^(k-1))*exp(1)^(-(i/A)^(k)))*8760}

WEA_pow_tot100<-reclassify(A100_200, c(-Inf,Inf,0))
for(i in 1:29){
  mean_wind<-reclassify(A100_200, c(-Inf,Inf,i))
  cp<-pow_curve$E.82_cp[i]
  cpe82<-reclassify(A100_200, c(-Inf,Inf,cp))
  rSTACK<-stack(airdens_200,cpe82,mean_wind,k100_200,A100_200)
  WEA_pow <-overlay(rSTACK, fun=fun_totE82, unstack=TRUE)
  WEA_pow_tot100<-WEA_pow_tot100+WEA_pow
}
#rel_diff_PEPP<-(WEA_pow_tot100/WEA_pow_tot125)

#150 meters above ground with V150-4.2 power curve (73m radius) with an efficiency parameter of 0.8 (mail philipp 12.5.20)
fun_totV150<-function(airdens_200,cpV150,i,k,A){0.8*(0.5*(airdens_200*(73^2*pi)*i^3)*cpV150)/1000*(k/A*((i/A)^(k-1))*exp(1)^(-(i/A)^(k)))*8760}

WEA_pow_tot150<-reclassify(A150_200, c(-Inf,Inf,0))
for(i in 1:29){
  mean_wind<-reclassify(A150_200, c(-Inf,Inf,i))
  cp1<-pow_curve$V150_cp[i]
  cpV150<-reclassify(A150_200, c(-Inf,Inf,cp1))
  rSTACK<-stack(airdens_200,cpV150,mean_wind,k150_200,A150_200)
  WEA_pow1 <-overlay(rSTACK, fun=fun_totV150, unstack=TRUE)
  WEA_pow_tot150<-WEA_pow_tot150+WEA_pow1
}



par(mfrow=c(2,2))
mapview(WEA_pow_tot125, alpha.regions = 0.8)
mapview(WEA_pow_tot100, alpha.regions = 0.8)
mapview(WEA_pow_tot150, alpha.regions = 0.8)


writeRaster(WEA_pow_tot125/1000,filename=paste(outpath,paste(cur_dat,"E138_200_MWH.tif",sep="_"),sep = "/"),overwrite=T)
writeRaster(WEA_pow_tot100/1000,filename=paste(outpath,paste(cur_dat,"E82_200MWH.tif",sep="_"),sep = "/"),overwrite=T)
writeRaster(WEA_pow_tot150/1000,filename=paste(outpath,paste(cur_dat,"V150_200MWH.tif",sep="_"),sep = "/"),overwrite=T)

```
For the total area of Switzerland, the V112-3.0 provides around 1500 TWh of physical potential energy. Including the Specific wind distribution, the height dependent air density and the turbine parameters. In 2012, meteotest assessed the physical wind energy potential for Switzerland for the BAFU (Cattin, 2012). They calculated about 4800 TWh of PEPP, but used an optimal rotor performance of 0.59. Our results are much closer to what a specific wind turbine can produce since we considered cp's according to the power curve between 0.2 and 0.4. 

# Create a hexagonal grids
For further analysis we need planning units (PU's) according to the dimensions of the wind Turbine. For Switzerland, Cattin, 2012 estimate the areas for a V112 to 0.36km2 and for the smaller V90 to 0.23km2. In order to represent the PU shape more naturally, we consider a hexagonal grid. For the E82 we calculate with a hex diameter of 500m, resulting in app. 6*the respective rotor diameter of 40m as a minimal distance to the next turbine. The same procedure for the E138 and V150.
```{r}

#boundary<-readOGR("input_data/CH_geom/CH_Grenze.shp")
#pgInsert(con,c("GEO_base_data","CH_boundaries"),boundary)

boundary<-pgGetGeom(conn = con,name = c("GEO_base_data","CH_boundaries"))
mapview(boundary)



#create hexagonal grids with the corresponding cellsizes (hexagon formula d2)
###E138

PU_E138<-st_make_grid(st_as_sfc(st_bbox(boundary)), what = "polygons", cellsize = 700, square = FALSE)
PU_E138<-st_as_sf(PU_E138)
PU_E138$PU_ID<-c(1:nrow(PU_E138))

hex_cenE138<-as(st_centroid(PU_E138),"Spatial")

### E82
PU_E82<-st_make_grid(st_as_sfc(st_bbox(boundary)), what = "polygons", cellsize = 500, square = FALSE, crs = "+init=epsg:21781")
PU_E82<-st_as_sf(PU_E82)
PU_E82$PU_ID<-c(1:nrow(PU_E82))
hex_cenE82<-as(st_centroid(PU_E82),"Spatial")


####V150
PU_V150<-st_make_grid(st_as_sfc(st_bbox(boundary)), what = "polygons", cellsize = 900, square = FALSE, crs = "+init=epsg:21781")
PU_V150<-st_as_sf(PU_V150)
PU_V150$PU_ID<-c(1:nrow(PU_V150))
hex_cenV150<-as(st_centroid(PU_V150),"Spatial")

#crop points with boundary of CH
hex_cenV150<-hex_cenV150[boundary,]
#E82
hex_cenE82<-hex_cenE82[boundary,]
#E138
hex_cenE138<-hex_cenE138[boundary,]

pgInsert(con,c("WT_PU_HEX","cen_V150"),hex_cenV150)
pgInsert(con,c("WT_PU_HEX","cen_E82"),hex_cenE82)
pgInsert(con,c("WT_PU_HEX","cen_E138"),hex_cenE138)
```


## ENERGYSCAPE landscape types
The three different wind turbine models should be located in three specific regions. The largest V150 mainly in the flat areas (PLAT_URB, PLAT_AGRI) and in the flat, large inner alpine valleys (ALP_URB). The E138 will be placed in the Jura and in the PRE_ALPS. The smalles E82 in the touristic alpine regions, the alpine areas with and without infrastructure.
```{r}

#import CH boundary to clip points
LT<-raster("input_data/BIOG_REG/LT3_rast1.tif")
LT<-projectRaster(LT, crs="+init=epsg:21781")

WEA_pow_tot150<-raster("intermediate_steps/1_wp/pot_ener_CH/2020-08-23_V150_200MWH.tif")
WEA_pow_tot125<-raster("intermediate_steps/1_wp/pot_ener_CH/2020-05-12_E138_200MWH.tif")
WEA_pow_tot100<-raster("intermediate_steps/1_wp/pot_ener_CH/2020-08-23_E82_200MWH.tif")

hex_cenV150$LT<-extract(LT,hex_cenV150)
hex_cenE138$LT<-extract(LT,hex_cenE138)
hex_cenE82$LT<-extract(LT,hex_cenE82)

hex_cenV150$prod_MW<-extract(WEA_pow_tot150/1000,hex_cenV150, fun=mean, buffer= 450)
hex_cenE138$prod_MW<-extract(WEA_pow_tot125/1000,hex_cenE138,fun=mean, buffer= 350)
hex_cenE82$prod_MW<-extract(WEA_pow_tot100/1000,hex_cenE82,fun=mean, buffer= 250)
#select only the appropriate sites for the WEA
hex_cenV150_sel<-subset(hex_cenV150,LT==1,)
hex_cenE82_sel<-subset(hex_cenE82,LT==2,)
hex_cenE138_sel<-subset(hex_cenE138,LT==3,)

#combine
cen_all<-rbind(hex_cenV150_sel,hex_cenE82_sel,hex_cenE138_sel)
pgInsert(con,c("WT_PU_HEX","cen_all_200825"),cen_all)

mapview(cen_all,zcol = "LT", burst = TRUE)

```
Interestingly, the selection based on LT produces some holes (not many) anyway, we therefore exported the hex_cenXY to arcmap and combined the layers there to one single layer cen_all

# Hexagonal points from Egli et a., 2017

 Hexagons with further informations (Egli et al. 2017)
Egli et al., 2017 calculated in a hexagonal grid further site specific values. The goal of this section is to compare the MAX wind value from Egli et al., 2017 with our calculated PEPP. (LT-1 = Mittelland, Lt2= Alpen, LT3 = Voralpen )


```{r}

#extract raster values alti
cen_all$alti<-extract(dem_200,hex_all)

#extract raster values airdens
cen_all$airdens<-extract(airdens_200,cen_all)

#extract respective MW from rasters and assign other values

for(i in 1:length(cen_all)){
if(cen_all$LT[i]==1){
  cen_all$WT_model[i]<-"V150_4.2"
}
  else if(cen_all$LT[i]==2){
  cen_all$WT_model[i]<-"E82_2.0"
}
  else{
  cen_all$WT_model[i]<-"E138_4.0"
  }
}
#all_cen<-readOGR("intermediate_steps/1_wp/2020-05-14_CEN_all_fin.shp")

pgInsert(con,c("WT_PU_HEX",paste("cen_all",cur_dat,sep = "_")),cen_all)
mapview(cen_all,zcol = "WT_model", burst = TRUE)
```
