---
title: "select_scenario"
author: "R.Spielhofer"
date: "23/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(raster)
require(rgdal)
require(snow)
require(mapview)
require(dplyr)
require(ggplot2)
require(sf)
require(sp)
require(ecr)
require(Hmisc)
require(tmap)
require(tmaptools)
require(DBI)
require(RPostgres)
require(rpostgis)
require(mapview)
require(maptools)
require(reticulate)
require(spatstat)
require(RPostgreSQL)


con<- dbConnect(Postgres(), dbname = "publication_3_fin", host = "localhost", user = "postgres", password
                        = "reto89LLSIMI")
```

##  choosing the scenario
In order to automate the optimization of many scenario we need to define the points the NSGA2 considers in each sceanario. We store the respective point data in the postgres SQL DB in the "scenario" schema. 


```{r}


cen<-st_read(dsn = con, Id(schema="WT_PU_HEX", table = "CEN_FIN_201008"))
#if necessary, subset the data for testing
#cen<-cen[2400:2600,]
cur_dat<-Sys.Date()
#NO_CONSTR B1
scen_name<-paste("B1",cur_dat,sep = "_")
st_write(obj = cen, dsn = con, Id(schema="scenario", table = scen_name))

##B1_BLN+ (no constrainst except not in BLN!!)
tmp<-subset(cen,cen$DIST_BLN > 0)
scen_name<-paste("B1_BLN+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

##B1_FFF+ (no constrainst except not in FFF!!)
tmp<-subset(cen,cen$FFF == 0)
scen_name<-paste("B1_FFF+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

##B1_FOR+ (no constrainst except not in FOR!!)
tmp<-subset(cen,cen$DIST_FOR > 0)
scen_name<-paste("B1_FOR+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


#B2 NO EXCLUSION AREAS
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 0)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_RAD>5000)
tmp<-subset(tmp,tmp$DIST_AIR>0)


scen_name<-paste("B2",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


#B2 NO EXCLUSION AREAS but allow WT in BLN

tmp<-subset(cen,cen$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 0)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_RAD>5000)
tmp<-subset(tmp,tmp$DIST_AIR>0)


scen_name<-paste("B2_BLN-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))



#B2 NO EXCLUSION AREAS and NOT in FOREST
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_FOR>0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 0)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_RAD>5000)
tmp<-subset(tmp,tmp$DIST_AIR>0)


scen_name<-paste("B2_FOR+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


#B2 NO EXCLUSION AREAS and NOT in FFF
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$FFF==0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 0)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_RAD>5000)
tmp<-subset(tmp,tmp$DIST_AIR>0)


scen_name<-paste("B2_FFF+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


## not exclusion and not reserve (B3)

tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)


scen_name<-paste("B3",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))



## B3_BLN- (vorb + restriction) but allow WT in BLN

tmp<-subset(cen,cen$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)


scen_name<-paste("B3_BLN-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


## B3_FOR+ (consider Ausschluss und Vorbehalt and restrict forests)

tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_FOR>0)

scen_name<-paste("B3_FOR+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

## B3_FFF+ (consider Ausschluss und Vorbehalt and restrict FFF)

tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$FFF==0)

scen_name<-paste("B3_FFF+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


## B3_ISOS+

tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_ISOS>1000)

scen_name<-paste("B3_ISOS+",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

#B4 including further constraints
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_FOR>0)
tmp<-subset(tmp,tmp$DIST_ISOS>1000)
tmp<-subset(tmp,tmp$FFF==0)

scen_name<-paste("B4",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

#B4_FFF- possible to build WT in FFF
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_FOR>0)
tmp<-subset(tmp,tmp$DIST_ISOS>1000)


scen_name<-paste("B4_FFF-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


#B4_ISOS- possible to build WT in ISOS
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_FOR>0)
tmp<-subset(tmp,tmp$FFF==0)

scen_name<-paste("B4_ISOS-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))


#B4_FOR- possible to build WT in forest
tmp<-subset(cen,cen$DIST_BLN > 0)
tmp<-subset(tmp,tmp$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$FFF==0)
tmp<-subset(tmp,tmp$DIST_ISOS>1000)

scen_name<-paste("B4_FOR-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

#B4 including further constraints without BLN

tmp<-subset(cen,cen$DIST_HZ>300)
tmp<-subset(tmp,tmp$DIST_UNE_K > 3000)
tmp<-subset(tmp,tmp$DIST_UNE_N>0)
tmp<-subset(tmp,tmp$DIST_MEAD > 0)
tmp<-subset(tmp,tmp$DIST_FLOOD > 0)
tmp<-subset(tmp,tmp$DIST_NATPA>2000)
tmp<-subset(tmp,tmp$DIST_VAEW>0)
tmp<-subset(tmp,tmp$DIST_MIL>100)
tmp<-subset(tmp,tmp$DIST_AIR>0)
tmp<-subset(tmp,tmp$DIST_REG_N>0)
tmp<-subset(tmp,tmp$DIST_BIOS>0)
tmp<-subset(tmp,tmp$DIST_JB>0)
tmp<-subset(tmp,tmp$DIST_RAD>20000)
tmp<-subset(tmp,tmp$DIST_FOR>0)
tmp<-subset(tmp,tmp$DIST_ISOS>1000)
tmp<-subset(tmp,tmp$FFF==0)

scen_name<-paste("B4_BLN-",cur_dat,sep = "_")
st_write(obj = tmp, dsn = con, Id(schema="scenario", table = scen_name))

```
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
