---
title: "Results and PLOTS wind optim project"
author: "R.Spielhofer"
date: "22 June 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("stringr")

require(raster)
require(rgdal)
require(dplyr)
require(sf)
require(sp)
require(ggplot2)
require(tmap)
require(tmaptools)
require(DBI)
require(RPostgreSQL)
require(rpostgis)
require(ggpubr)
require(spatstat)
require(gdalUtils)
require(reticulate)
require(tidyr)
require(maptools)
require(RPostgres)
require(stringr)
require(car)
library(onewaytests)
require(rstatix)
require(ggsci)
```

## Data read in
```{r}
in_dat<-read.csv("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/all_201019.csv")
cur_dat<-Sys.Date()

in_dat$group<-as.factor(in_dat$group)
group_names<-levels(in_dat$group)
in_dat$SCENARIO<-as.factor(in_dat$SCENARIO)
scen_names<-levels(in_dat$SCENARIO)
in_dat$frame_policy<-as.factor(in_dat$frame_policy)
in_dat$restr<-as.factor(in_dat$restr)


in_dat$restr <- factor(in_dat$restr,levels = c( "base","-","+"))
in_dat$frame_policy <- factor(in_dat$frame_policy,levels = c("B1","B2","B3","B4"))
frame_names<-levels(in_dat$frame_policy)

conn <- dbConnect(Postgres(), dbname = "publication_3_fin", host = "localhost", port = 5432, 
                      user = "postgres", password = "reto89LLSIMI")

scen_names<-dbGetQuery(conn,"SELECT table_name FROM information_schema.tables WHERE table_schema='optim_res_201005'")

B1<-st_read(dsn = conn, Id(schema="optim_res_201005", table = as.character(scen_names[23,])))
B2<-st_read(dsn = conn, Id(schema="optim_res_201005", table = as.character(scen_names[14,])))
B3<-st_read(dsn = conn, Id(schema="optim_res_201005", table = as.character(scen_names[9,])))
B4<-st_read(dsn = conn, Id(schema="optim_res_201005", table = as.character(scen_names[18,])))


bound<-st_read(dsn= conn, Id(schema="GEO_base_data", table = "CH_boundaries"))
bound<-st_transform(bound,crs = "+init=epsg:21781") 
```


##some maps

You can also embed plots, for example:

```{r pressure, echo=FALSE}


#interactive
mapview::mapview(B1,zcol="prod_MW")




map_tmp<-ggplot(data = bound) +
    geom_sf() +
     geom_sf(data = B4, aes(color = prod_MW))

#B4 and KIBK
df_B4<-st_drop_geometry(B4)
hist(df_B4$KIBK)
    
```

##First question
"What is the effect on (n_WT, clustering, energy density) between the four national frame policies (B1,B2,B3,B4)"


```{r}

#1. What is the effect on (n_WT, clustering, energy density) between the three national frame policies (B1,B2,B3,B4)
#subsetting for testing
d<-subset(in_dat,in_dat$SCENARIO=="B1")
a<-subset(in_dat,in_dat$SCENARIO=="B2")
b<-subset(in_dat,in_dat$SCENARIO=="B3")
c<-subset(in_dat,in_dat$SCENARIO=="B4")
my_comparisons <- list( c("B1", "B2"), c("B1", "B3"), c("B1", "B4"), c("B2", "B3"), c("B2", "B4"), c("B3", "B4") )

all<-rbind(a,b,c,d)

### Number of WT
#1. CHECK FOR NORMAL distribution

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT)

 #homogeneity of variance
levene_test(all,number_WT~frame_policy,center = mean)

#since the normality is not strongly violated, we have 80 records per group and variance homogeneity, we assume ANOVA preconditions as given:

anov<-aov(number_WT~frame_policy,data=all)
compare_means(number_WT~frame_policy,data = all, method = "anova")


#graphical check
a<-ggboxplot(all, x = "SCENARIO", y = "number_WT", 
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", ref.group = "B1", 
                     method = "t.test" )+
  stat_compare_means(label.y = 1200,method="anova") #the global


## CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

levene_test(all,CE_index~frame_policy,center = mean) #homogeneity of variance

#graphical check
b<-ggboxplot(all, x = "SCENARIO", y = "CE_index", 
        ylab = "CE_ind", xlab = "SCENARIO")+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                     ref.group = "B1", method="t.test" )+
  stat_compare_means(label.y = .5, method = "anova")

anov<-aov(CE_index~frame_policy,data=all)
summary(anov)
TukeyHSD(anov,"frame_policy")


## enerdens
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

levene_test(all,mean_MWH.yHA~frame_policy,center = mean) #homogeneity of variance is given

#since homogeneity of variance is not given and we have violations of normality, we perform a Welch-Test
#if levene p<.05 thus a welch test should be performed, since variances are not homogen
compare_means(mean_MWH.yHA~SCENARIO,all)



#graphical check
c<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA", 
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                     ref.group = "B1" )+
  stat_compare_means(label.y = 1.1)

plot_tmp<-ggarrange(a, b, c,  ncol = 1,nrow = 3, labels = "auto")


jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q1/",paste(cur_dat,"all.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()

## B4 is different from all other, B1,B2,B3 have equal energy densities

```

## common point B1, B2, B4, B4
```{r}
conn <- dbConnect(Postgres(), dbname = "publication_3_fin", host = "localhost", port = 5432, 
                      user = "postgres", password = "reto89LLSIMI")

a<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B1_2020-10-09_res"))
tmpA<-subset(a,a$sum_pop_pareto==80)
b<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B2_2020-10-08_res"))
tmpB<-subset(b,b$sum_pop_pareto==80)
c<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B3_2020-10-08_res"))
tmpC<-subset(c,c$sum_pop_pareto==80)
d<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B4_2020-10-10_res"))
tmpD<-subset(d,d$sum_pop_pareto==80)

g<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B4_FFF-_2020-10-08_res"))
tmpG<-subset(g,g$sum_pop_pareto==80)

#all together
all<-rbind(tmpC,tmpD)
count_ID<-all%>%count(WT_ID)

commonB3_B4<-all[duplicated(all$WT_ID), ]
all_common<-all[!duplicated(all$WT_ID), ]

map_sec<-ggplot(commonB3_B4) +
    geom_sf(data = bound, fill = NA, color = "gray", size=.8)+
    geom_sf(data = commonB3_B4)
    theme_light()+
   theme(axis.text=element_text(size=10))

jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/maps/sec_maps/",paste(ScenName,"_sec_pareto_map.jpg",sep=""),sep=""),width = 1200, height = 1200,res=300)
plot(map_sec)
dev.off()
```



## Second question (s)
2.1 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the FOREST from WT?

```{r}
#
#subsetting FOREST

all<-subset(in_dat, in_dat$SCENARIO=="B3_FOR+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_ISOS-" | in_dat$SCENARIO=="B4_FFF-")

all$SCENARIO<-recode(all$SCENARIO,"B4_ISOS-" = "B3_FOR+_FFF+", "B4_FFF-" = "B3_FOR+_ISOS+" )
 ord <- c("B3","B3_FOR+","B3_FOR+_ISOS+","B3_FOR+_FFF+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_FOR+"), c("B3_FOR+", "B3_FOR+_ISOS+"),c("B3_FOR+", "B3_FOR+_FFF+"), c("B3_FOR+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                      method="t.test" )+
 theme(legend.position = "none")

############################ CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
  theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA", 
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
  theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp

jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```


2.2 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the ISOS from WT?

```{r}
#
#subsetting ISOS

all<-subset(in_dat, in_dat$SCENARIO=="B3_ISOS+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_FFF-" | in_dat$SCENARIO=="B4_FOR-")

all$SCENARIO<-recode(all$SCENARIO,"B4_FOR-" = "B3_ISOS+_FFF+", "B4_FFF-" = "B3_ISOS+_FOR+" )

ord <- c("B3","B3_ISOS+","B3_ISOS+_FOR+","B3_ISOS+_FFF+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_ISOS+"), c("B3_ISOS+", "B3_ISOS+_FOR+"),c("B3_ISOS+", "B3_ISOS+_FFF+"), c("B3_ISOS+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                      method="t.test" )+
  theme(legend.position = "none")

############################ CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
         theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA",
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
    theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp


jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```

2.3 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the FFF from WT?

```{r}
#
#subsetting FFF

all<-subset(in_dat, in_dat$SCENARIO=="B3_FFF+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_ISOS-" | in_dat$SCENARIO=="B4_FOR-")

all$SCENARIO<-recode(all$SCENARIO,"B4_FOR-" = "B3_FFF+_ISOS+", "B4_ISOS-" = "B3_FFF+_FOR+" )

ord <- c("B3","B3_FFF+","B3_FFF+_FOR+","B3_FFF+_ISOS+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_FFF+"), c("B3_FFF+", "B3_FFF+_FOR+"),c("B3_FFF+", "B3_FFF+_ISOS+"), c("B3_FFF+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
      theme(legend.position = "none")

########################### CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
        theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA",
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
        theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp

jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```


##Effects

```{r}
in_dat<-read.csv("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/all_201019_Q2.csv")

#first instance (B3_FIR+, B3_FFF+, B3_ISOS)
all<-subset(in_dat, in_dat$SCENARIO=="B3_FFF+" |  in_dat$SCENARIO=="B3_FOR+" | in_dat$SCENARIO=="B3_ISOS+" | in_dat$SCENARIO=="B3")
summary(aov(number_WT~group,all))

my_comparisons <- list( c("B3_FOR+", "B3_FFF+"), c("B3_FOR+", "B3_ISOS+"),c("B3_ISOS+", "B3_FFF+"),c("B3_FOR+", "B3"), c("B3", "B3_ISOS+"),c("B3", "B3_FFF+"))
pairwise.t.test(in_dat$number_WT, in_dat$SCENARIO, p.adj = "none")
pairwise.t.test(in_dat$CE_index, in_dat$SCENARIO, p.adj = "none")
pairwise.t.test(in_dat$mean_MWH.yHA, in_dat$SCENARIO, p.adj = "none")
compare_means(number_WT~SCENARIO,in_dat)

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
      theme(legend.position = "none")

### Number CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems to have +- equal variances between scen

compare_means(CE_index~SCENARIO,all)

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
        theme(legend.position = "none")

### Number enerdens
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,mean_MWH.yHA~SCENARIO,center = mean) #seems to have +- equal variances between scen

compare_means(mean_MWH.yHA~SCENARIO,all)

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA",
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
        theme(legend.position = "none")

### effect of instance
summary(aov(number_WT~group+instance,in_dat))
compare_means(number_WT~instance,in_dat, )
welch.test(number_WT~instance,in_dat)

```
```{r}
conn <- dbConnect(Postgres(), dbname = "publication_3_fin", host = "localhost", port = 5432, 
                      user = "postgres", password = "reto89LLSIMI")

B3_FOR<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B3_FOR+_2020-10-08_res"))

B3<-st_read(dsn = conn, Id(schema="optim_res_201005", table = "B3_2020-10-08_res"))

tmp_joined <- st_join(B3,B3_FOR)
tmp_joined <-tmp_joined [,-c(43:83)]
names(tmp_joined)[names(tmp_joined) == "sum_pop_pareto.y"] <- "sum_popPAR_B3_FOR"
names(tmp_joined)[names(tmp_joined) == "sum_pop_pareto.x"] <- "sum_popPAR_B3"
tmp_joined[c("sum_popPAR_B3_FOR")][is.na(tmp_joined[c("sum_popPAR_B3_FOR")])] <- 0
tmp_joined$delta<-tmp_joined$sum_popPAR_B3-tmp_joined$sum_popPAR_B3_FOR
tmpINFOR<-subset(tmp_joined,tmp_joined$DIST_FOR.x<1)
mapview::mapview(tmpINFOR,zcol="delta")

```


