---
title: "Results and PLOTS wind optim project"
author: "R.Spielhofer"
date: "22 June 2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(raster)
require(rgdal)
require(dplyr)
require(sf)
require(sp)
require(ggplot2)
require(tmap)
require(tmaptools)
require(DBI)
require(RPostgreSQL)
require(rpostgis)
require(ggpubr)
require(spatstat)
require(gdalUtils)
require(reticulate)
require(tidyr)
require(maptools)
require(RPostgres)
require(stringr)
require(car)
library(onewaytests)
require(rstatix)
require(ggsci)
require(caret)
```

## Data read in
```{r}
in_dat<-read.csv("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/TEST_FOR_201026_B.csv")
cur_dat<-Sys.Date()

in_dat$SCENARIO<-as.factor(in_dat$SCENARIO)
scen_names<-levels(in_dat$SCENARIO)


conn <- dbConnect(Postgres(), dbname = "publication_3_fin", host = "localhost", port = 5432, 
                      user = "postgres", password = "reto89LLSIMI")

scen_names<-dbGetQuery(conn,"SELECT table_name FROM information_schema.tables WHERE table_schema='optim_res_201005'")


B3<-st_read(dsn = conn, Id(schema="optim_res_201022", table = "B3_201026_60K"))
B3_FOR<-st_read(dsn = conn, Id(schema="optim_res_201022", table = "B3_FOR+_201026_60K"))
B3_1027<-st_read(dsn = conn, Id(schema="optim_res_201022", table = "B3_60k_1027"))


bound<-st_read(dsn= conn, Id(schema="GEO_base_data", table = "CH_boundaries"))
bound<-st_transform(bound,crs = "+init=epsg:21781") 
```


##some maps

You can also embed plots, for example:

```{r pressure, echo=FALSE}


#interactive
mapview::mapview(B1,zcol="prod_MW")

map_tmp<-ggplot(data = bound) +
    geom_sf() +
     geom_sf(data = B4, aes(color = prod_MW))

#B4 and KIBK
df_B4<-st_drop_geometry(B4)
hist(df_B4$KIBK)
    
```

##First question
"What is the effect on (n_WT, clustering, energy density) between the four national frame policies (B1,B2,B3,B4)"


```{r}

#1. What is the effect on (n_WT, clustering, energy density) between the three national frame policies (B1,B2,B3,B4)
#subsetting for testing

b<-subset(in_dat,in_dat$SCENARIO=="B3")
c<-subset(in_dat,in_dat$SCENARIO=="B3_FOR+")
my_comparisons <- list( c("B3", "B3_FOR+") )

all<-rbind(c,b)

### Number of WT
#1. CHECK FOR NORMAL distribution

in_dat %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT)

 #homogeneity of variance
levene_test(in_dat,number_WT~SCENARIO,center = mean)

#since the normality is not strongly violated, we have 80 records per group and variance homogeneity, we assume ANOVA preconditions as given:

anov<-aov(number_WT~frame_policy,data=all)
compare_means(number_WT~frame_policy,data = all, method = "anova")


#graphical check
a<-ggboxplot(in_dat, x = "SCENARIO", y = "number_WT", 
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", ref.group = "B3", 
                     method = "t.test" )+
  stat_compare_means(label.y = 1200,method="anova") #the global


## CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

levene_test(all,CE_index~frame_policy,center = mean) #homogeneity of variance

#graphical check
b<-ggboxplot(in_dat, x = "SCENARIO", y = "CE_index", 
        ylab = "CE_ind", xlab = "SCENARIO")+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                     ref.group = "B1", method="t.test" )+
  stat_compare_means(label.y = .5, method = "anova")

anov<-aov(CE_index~frame_policy,data=all)
summary(anov)
TukeyHSD(anov,"frame_policy")


## enerdens
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

levene_test(all,mean_MWH.yHA~frame_policy,center = mean) #homogeneity of variance is given

#since homogeneity of variance is not given and we have violations of normality, we perform a Welch-Test
#if levene p<.05 thus a welch test should be performed, since variances are not homogen
compare_means(mean_MWH.yHA~SCENARIO,all)



#graphical check
c<-ggboxplot(in_dat, x = "SCENARIO", y = "mean_MWH.yHA", 
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
   stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                     ref.group = "B1" )+
  stat_compare_means(label.y = 1.1)

plot_tmp<-ggarrange(a, b, c,  ncol = 1,nrow = 3, labels = "auto")


jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q1/",paste(cur_dat,"all.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()

## B4 is different from all other, B1,B2,B3 have equal energy densities

```



## Second question (s)
2.1 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the FOREST from WT?

```{r}
#
#subsetting FOREST

all<-subset(in_dat, in_dat$SCENARIO=="B3_FOR+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_ISOS-" | in_dat$SCENARIO=="B4_FFF-")

all$SCENARIO<-recode(all$SCENARIO,"B4_ISOS-" = "B3_FOR+_FFF+", "B4_FFF-" = "B3_FOR+_ISOS+" )
 ord <- c("B3","B3_FOR+","B3_FOR+_ISOS+","B3_FOR+_FFF+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_FOR+"), c("B3_FOR+", "B3_FOR+_ISOS+"),c("B3_FOR+", "B3_FOR+_FFF+"), c("B3_FOR+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                      method="t.test" )+
 theme(legend.position = "none")

############################ CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
  theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA", 
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
  theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp

jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```


2.2 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the ISOS from WT?

```{r}
#
#subsetting ISOS

all<-subset(in_dat, in_dat$SCENARIO=="B3_ISOS+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_FFF-" | in_dat$SCENARIO=="B4_FOR-")

all$SCENARIO<-recode(all$SCENARIO,"B4_FOR-" = "B3_ISOS+_FFF+", "B4_FFF-" = "B3_ISOS+_FOR+" )

ord <- c("B3","B3_ISOS+","B3_ISOS+_FOR+","B3_ISOS+_FFF+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_ISOS+"), c("B3_ISOS+", "B3_ISOS+_FOR+"),c("B3_ISOS+", "B3_ISOS+_FFF+"), c("B3_ISOS+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif",
                      method="t.test" )+
  theme(legend.position = "none")

############################ CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
         theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA",
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
    theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp


jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```

2.3 What is the effect on (n_WT, clustering, energy density) when protecting or allowing the FFF from WT?

```{r}
#
#subsetting FFF

all<-subset(in_dat, in_dat$SCENARIO=="B3_FFF+" |  in_dat$SCENARIO=="B3" | in_dat$SCENARIO=="B4" | in_dat$SCENARIO=="B4_ISOS-" | in_dat$SCENARIO=="B4_FOR-")

all$SCENARIO<-recode(all$SCENARIO,"B4_FOR-" = "B3_FFF+_ISOS+", "B4_ISOS-" = "B3_FFF+_FOR+" )

ord <- c("B3","B3_FFF+","B3_FFF+_FOR+","B3_FFF+_ISOS+","B4")
all$SCENARIO <- factor(all$SCENARIO,levels=ord)


my_comparisons <- list( c("B3", "B3_FFF+"), c("B3_FFF+", "B3_FFF+_FOR+"),c("B3_FFF+", "B3_FFF+_ISOS+"), c("B3_FFF+", "B4"))

### Number of WT
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(number_WT) #not normally distributed but not strongly violated
# homogeneity of var
levene_test(all,number_WT~SCENARIO,center = mean) #seems to have +- equal variances between scen

#graphical check
nWT<-ggboxplot(all, x = "SCENARIO", y = "number_WT",
        ylab = "n_WT", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
      theme(legend.position = "none")

########################### CE
#1. CHECK FOR NORMAL DISTR
all %>%
  group_by(SCENARIO) %>%
  shapiro_test(CE_index)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
CE<-ggboxplot(all, x = "SCENARIO", y = "CE_index",
        ylab = "CE_ind", xlab = "SCENARIO")+
        stat_compare_means(comparisons = my_comparisons, label = "p.signif")+
        theme(legend.position = "none")

################# enerdens
#1. CHECK FOR NORMAL DISTR

all %>%
  group_by(SCENARIO) %>%
  shapiro_test(mean_MWH.yHA)

# homogeneity of var
levene_test(all,CE_index~SCENARIO,center = mean) #seems non equal variances between scenarios --> wilcox and Kruskal wallis

#graphical check
enerdens<-ggboxplot(all, x = "SCENARIO", y = "mean_MWH.yHA",
        ylab = "mean_MWH.yHA", xlab = "SCENARIO")+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif" )+
        theme(legend.position = "none")

plot_tmp<-ggarrange(nWT, CE, enerdens,  ncol = 3,nrow = 1, labels = c("Min number WT", "best clustering (min)", "Max energy density"))
plot_tmp

jpeg(file=paste("D:/04_PROJECTS/2001_WIND_OPTIM/WIND_OPTIM_git/intermediate_steps/3_wp/OPTIM_RES/results_stat/Q2/",paste(cur_dat,"FOR.jpg",sep="_"),sep=""),width = 1500, height = 1000)
plot(plot_tmp)
dev.off()
```

## security analysis I
Which wind turbines in restricted areas (FOR, FFF or ISOS) are of interest in order to support the overall optimized allocation goal?
```{r}

#merge the two data frames

B_join<-st_join(B3, B3_FOR)
B_join<-B_join[,-c(43:84)]
names(B_join)[names(B_join) == "rel_arch_nonDOM.y"] <- "rel_arch_B3_FOR"
B_join[c("rel_arch_B3_FOR")][is.na(B_join[c("rel_arch_B3_FOR")])] <- 0


#we calculate the difference between the "security" of wind turbines of B3 and B3_FOR+
B_join$delt_B3_B3FOR<-B_join$rel_arch_nonDOM.x-B_join$rel_arch_B3_FOR

mapview::mapview(subset(B_join,B_join$rel_arch_nonDOM.x>.85),zcol="rel_arch_nonDOM.x")

#subset the within and a not within WT locations
IN_FOR<-subset(B_join,B_join$DIST_FOR.x<1)
NOT_INFOR<-subset(B_join,B_join$DIST_FOR.x>1)

#map the not in forest points according to their differences of the scenarios
#++ values indicate that the WT is very important in B3 but not when FOR is restricted in B3_FOR+
#-- WT is very important when restricting FOR but not when FOR everything is allowed.
mapview::mapview(subset(NOT_INFOR,NOT_INFOR$delt_B3_B3FOR>.5 | NOT_INFOR$delt_B3_B3FOR<.5*-1),zcol="delt_B3_B3FOR")

#map the differences between B3 and B3_FOR+
# in FOREST
mapview::mapview(subset(B_join,B_join$DIST_FOR.x<1),zcol="delt_B3_B3FOR")
#the high positive values show important points within forests in SCENARIO B3

#not in FOREST
mapview::mapview(subset(B_join,B_join$DIST_FOR.x>1 & (B_join$delt_B3_B3FOR<0.5*-1| B_join$delt_B3_B3FOR>0.5)),zcol="delt_B3_B3FOR")
#the low negative values show that the WT is not important in the B3 scenario, but becomes very important when restricting the forest

###show optimal, secure solutions within B3 to fulfill the 4.3 TWH/y
tmpA<-B_join[with(B_join, order(B_join$rel_arch_nonDOM.x,decreasing = T)), ]

#while loop to sum prod MW until 4300000 MWh/y is reached
sum_prod = 0
ind=0

for(i in 1:nrow(tmpA)){
 if(sum_prod>4300000){
   break
   print(i)
  }
  tmp_prod<-tmpA$prod_MW[i]
  sum_prod<-sum_prod+tmp_prod
}

#create a subset to map  
tmpA<-tmpA[1:i,]

tmpA%>%tmpA$DIST_FOR.x<1
mapview::mapview(tmpA,zcol="delt_B3_B3FOR")


```

#what makes the WT positive or negative?
```{r}
nonSp<-st_drop_geometry(B_join)

preProcess_range_model <- preProcess(nonSp[,c(4:15,17:24,26:30,32,34,35,45)], 
                        method = c("center", "scale", "nzv"))
preProcess_range_model$method

PRED <- predict(preProcess_range_model, newdata = nonSp[,c(4:15,17:24,26:30,32,34,35,45)])


# Step 1: Get row numbers for the training data
trainRowNumbers <- createDataPartition(PRED$delt_B3_B3FOR, p=0.7, list=FALSE)
# Step 2: Create the training  dataset
trainset <- PRED[trainRowNumbers,]
# Step 3: Create the test dataset
testset <- PRED[-trainRowNumbers,]

outcomeName <- variable.names(PRED[29])
pred_names<-variable.names(PRED[,c(1:28)])
# Define the train control
fitControl <- trainControl(method = "repeatedcv", number = 10, repeats = 3, savePredictions = T,   verboseIter = FALSE)

##----------RF tune
mtry <- sqrt(ncol(trainset[,pred_names]))
RFtune <- expand.grid(mtry=mtry)
#simple
start<-Sys.time()
#rf_mod<-train(trainset[,pred_names],  as.factor(trainset[,outcomeName]), method = "rf")
rf_B3<-train(trainset[,pred_names],  trainset[,outcomeName], method = "rf",trControl = fitControl,tunegrid=RFtune)
end<-Sys.time()
end-start

varimp_B3 <- varImp(rf_B3)
plot(varimp_B3)
VARIMP_B3<-varimp_B3$importance
write.csv(VARIMP_B3,"C:/Users/spreto/Desktop/B3.csv")
```

##variable importance with other statistics
```{r}
B_join$sec_catB3[B_join$delt_B3_B3FOR< 0] <- "wt_imp_plusFOR"
B_join$sec_catB3[B_join$delt_B3_B3FOR> 0] <- "wt_imp_B3"

# Convert the column to a factor
B_join$sec_catB3 <- factor(B_join$sec_catB3)
B_join<-st_drop_geometry(B_join)

B_join<-B_join[,c(4:15,17:24,26:30,32,34,35,46)]

mod<-list()
for(i in 1:28){
    fmla <- formula(paste(names(B_join)[i], " ~ sec_catB3"))
    mod[[i]]<-wilcox.test(fmla, data = B_join, paired = FALSE)
}

tapply(B_join$DIST_UNE_N.x,B_join$sec_cat,mean)
```

